Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-30 method.tex
Some small changes
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@782 ccdd05d5-56c1-461a-bf98-85f6876523b4

Inspiral signals are parameterized by a set of intrinsic parameters
$\bar{\theta}$ that determine the amplitude and phase evolution of the observed
binary signals. For systems where the effects of spin can be ignored, the
intrinsic parameters are the component masses of the binary, $\bar{\theta} =
(m_1, m_2)$. Searches for gravitational waves from compact binary coalescence
typically employ matched filter banks that discretely
sample the possible intrinsic parameters~\cite{findchirppaper}.  The filters
for the waveforms $x(t,\bar{\theta})$, known as templates, are the waveforms
weighted by the inverse detector noise amplitude spectral density, so as to
whiten them. To construct a template bank, templates are chosen with discrete
signal parameters $\theta_1,\, \theta_2,\, \cdots$, $\theta_N$ to assure a
bounded loss of \SNR~\cite{Owen:1995tm,Owen:1998dk}. That is, any possible
signal within the search space will have a cross-correlation of $\geq0.97$ with
at least one template. Such a template bank is said to have a 97\% {\em
minimum match}. Data are filtered against each template to produce an \SNR{}
time-series. Local peak-finding across time and templates determines detection
candidates.
%
\footnote{There are two gravitational-wave polarizations, $+$ and $\times$. A
given detector will observe a combination of these polarizations that will
largely be degenerate with an overall unknown constant phase.  This can be
maximized over by filtering for quadrature phases and taking the magnitude of
the result. For simplicity we will ignore that aspect in this work, as it is
straightforward to generalize but not necessary for understanding any of the
points that will be made.}

>>>>

Inspiral signals are parameterized by a set of intrinsic parameters
$\bar{\theta}$%
%
\editorial{Change this to a harpoon or vector symbol.}
%
that determine the amplitude and phase evolution of the gravitational wave strain. For systems where the effects of spin can be ignored, the
intrinsic parameters are the component masses of the binary, $\bar{\theta} =
(m_1, m_2)$. Searches for gravitational waves from compact binary coalescence
typically employ matched filter banks that discretely
sample the possible intrinsic parameters~\cite{findchirppaper}.  The filters
for the waveforms $h(t,\bar{\theta})$, known as templates, are the waveforms
weighted by the inverse detector noise amplitude spectral density. To construct a template bank, templates are chosen with discrete signal parameters $\theta_1,\, \theta_2,\, \cdots$, $\theta_N$ to assure a
bounded loss of \SNR~\cite{Owen:1995tm,Owen:1998dk}. That is, any possible
signal within the search space will have a cross-correlation of $\geq0.97$ with
at least one template. Such a template bank is said to have a {\em
minimum match} of 0.97. Data are filtered against each template to produce an \SNR{}
time-series. Local peak-finding across time and templates determines detection
candidates.
%
\footnote{There are two gravitational-wave polarizations, $+$ and $\times$. A
given detector will observe a combination of these polarizations that will
largely be degenerate with an overall unknown constant phase.  This can be
maximized over by filtering for quadrature phases and taking the magnitude of
the result. For simplicity we will ignore that aspect in this work, as it is
straightforward to generalize but not necessary for understanding any of the
points that will be made.}
